Comments on the revised version

### 2018-03-07 paper/revision2.tex
zmk fix for the S/L inversion

\textbf{Last paragraph of 1.2 is the third repetition of this.  It is redundant, despite the fact that some reviewer didn't get
it.
}

\textbf{In sect 5.1 you explain that you set lambda=1 because due to the resampling the distributions are stationary.  That is
correct.  But it would have been good to also conduct simulations on the original traces, which are probably not
stationary, and therefore there is more to gain from switching between policies.
Also, instead of starting the simulation of each period from an empty system, why not start from the situation at the
end of the previous period?
}

\textbf{Typo at end of 6.1.3: sentence with [24] appears twice.
}

@@

\textbf{The authors present a study based on a selection of several strategies and parameters. They execute several simulations
and show that using a feedback mechanism improvements over the standard approach without feedback are possible. This
results is not surprising considering previous results some of which are referenced within the manuscript. It must be
noted that the authors do not suggest a specific new scheduling algorithm and show that this algorithm results in
significant improvements over existing methods.
}

@@

>>>>

\textbf{Last paragraph of 1.2 is the third repetition of this.  It is redundant, despite the fact that some reviewer didn't get
it.
}
You are right. We rephrased this in a more neutral way.

\textbf{In sect 5.1 you explain that you set lambda=1 because due to the resampling the distributions are stationary.  That is
correct.  But it would have been good to also conduct simulations on the original traces, which are probably not
stationary, and therefore there is more to gain from switching between policies.
Also, instead of starting the simulation of each period from an empty system, why not start from the situation at the
end of the previous period?
}
Regarding your first point, good remark, we based this experimental design around previous results
from "Tuning Backfilling Queues"(JSSPP17) that show some degree of stationarity. We indeed
expect that non-stationary policy adaptation may allow more improvements (while
being harder to achieve). We made this clearer in the text.

Your second point is also relevant, yes that should perhaps slightly improve the results.
But we can see that the 'full feedback' simulated policy here is almost as good as the best
policy in the set, so we did not worry about this. In a non-stationary case, it may indeed
be necessary to properly take care of this.

\textbf{Typo at end of 6.1.3: sentence with [24] appears twice.
}
Right, we fixed this.

@@

\textbf{The authors present a study based on a selection of several strategies and parameters. They execute several simulations
and show that using a feedback mechanism improvements over the standard approach without feedback are possible. This
results is not surprising considering previous results some of which are referenced within the manuscript. It must be
noted that the authors do not suggest a specific new scheduling algorithm and show that this algorithm results in
significant improvements over existing methods.
}
We regret that the detailed answer of the previous rebuttal did not convince you. We disagree with this statement. We indeed
provide a new scheduling algorithm, which adapts to the situation by selecting the correct reordering policy. This algorithm
results in significant improvements over existing methods.
Thank you for your in-depth remarks once again. We integrated these into the minor revision.

@@

First of all, we corrected a crucial typographical error in the text. The S and
L were inverted in both Table 3 and Figure 4. This resolves a blatant
consistency issue with other publications, most crucially "Tuning Backfilling
Queues"(JSSPP17).

Indeed, the SQF policy works quite well on the traces considered here on average, and
under this resampling scheme. The variability however, is high, and it is not the best
on other traces.
It would indeed be interesting to have an experimental evaluation of exactly how much
one gains on average by choosing the bandit over a leave-one-trace-out majority vote policy
choice.

However, a good estimation of this quantity requires using more traces, and perhaps factoring
in the topology model of the machines, which should increase the heterogeneity between platforms
and therefore increase the dependence of the simulation performance on the trace/platform.
Such a study would be much more tedious.
Here, we prove the feasibility of the approach. The need for adaptivity is actually understated
by our simulation approach.
